Proposal full title \\ Proposal Acronym

### 2001-10-09 drafts/IST/PartC.tex
layout fix
svn path=/trunk/; revision=1462
toc
svn path=/trunk/; revision=1500
Riek CV
svn path=/trunk/; revision=1502

@@

@@

\chapter*{B5. Management}
\textit[This section, not exceeding two pages, should describe how the Take-Up

@@

Support Node or Cluster will require co-operation with other actions.

@@

@@

@@

\\ \\ to be written
\chapter{C8. Economic development and scientific and technological prospects}

>>>>

\addcontentsline{toc}{chapter}{C3. Community added value and contribution to EC policies}

@@

\addcontentsline{toc}{chapter}{C4. Contribution to Community social objectives}
\

@@

\chapter*{C5. Management}
\addcontentsline{toc}{chapter}{C5. Management}
\textit{This section, not exceeding two pages, should describe how the Take-Up

@@

Support Node or Cluster will require co-operation with other actions.}

@@

\addcontentsline{toc}{chapter}{C6. Description of the consortium}

@@

\addcontentsline{toc}{chapter}{C7. Descriptions of the participants}

@@

%% ALCOVE DE
\section*{Daniel Riek - Alcove Deutschland CTO}
Daniel Riek switched to GNU/Linux in late 1993 short after graduating
from school. In early 1997 during his studies of computing science at the
university of Bonn he founded the Linux service company ID-PRO together
with some friends. During the next years he worked as a developer and
engineer, later he served in the management area of ID-PRO. After ID-PRO
received a major venture capital financing, Daniel became the chairman
and speaker of the board of directors. There he was responsible for the
technical strategy, representation, the community and public relationship.
He also was, together with the companies CTO, responsible for the technical
support and the software development activities of the company.
Caused by the capital market crisis in late 2000 ID-PRO failed to acquire
new funds, that would have been necessary due to the venture capital driven
strategy. After a short rest Daniel joined Alcove to continue his work in
the Free Software business. Daniel is a strong supporter of the Free
Software Foundation Europe and is a member of the board of germany's Linux
vendors association Linux-Verband LIVE e.V.
Next contributors : Christian, Jaime.
\chapter*{C8. Economic development and scientific and technological prospects}
\addcontentsline{toc}{chapter}{C8. Economic development and scientific and
technological prospecs}
